df_scripted

### 2023-05-11 Tests/1. tests/an_test.Rmd
rename 2. tests

ggplot(df_scripted %>% filter(!is.na(HLEV2G_2)), aes(x = CFATINC, y = HLEV2G_2)) +
  geom_point() +
  stat_smooth(method = "glm", color = "red", se = FALSE,
              method.args = list(family = binomial)) +
  labs(
    title = "Salaire net selon le niveau d'éducation", 
    x = "Salaire net", 
    y = "Diplôme universitaire (0 = non ; 1 = oui)") +
  theme_few()
```

>>>>

ggplot(df_scripted %>% filter(!is.na(HLEV2G_2)), aes(x = CFATINC, y = HLEV2G_2)) +
  geom_point() +
  stat_smooth(method = "glm", color = "red", se = FALSE,
              method.args = list(family = binomial)) +
  labs(
    title = "Salaire net selon le niveau d'éducation", 
    x = "Salaire net", 
    y = "Diplome universitaire (0 = non ; 1 = oui)") +
  theme_few()
```
